### 2014-03-08 docs/seminar/casestudy.tex
revising

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure\ref{fig:architecture}. The client submits a document and searches for translators with a specific target language. Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator. The ranking system processes the calculated values and the offers the most related translators to the client.

@@

The \textit{Profiler} is responsible for accumulating personal information, translators' preferences, offered price and translation duration per word. The \textit{Ranking} system uses Learning to Rank techniques to return the most related translators to the client. The training data is provided by a group of annotators who are familiar with business of company using an evaluation system. The evaluation system suggests three translators and the annotators rate them by comparing between their factors. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section \ref{sec:apply}. The \textit{Proficiency Estimator} system stores the previous-translated documents in the cloud and indexes them using Lucene library. The similarity between query and indexed documents is used as a basis for estimation of translator's proficiency. In order to find proficiency value, the platform aggregates the similarity scores. The applied aggregation function is described in Section \ref{sec:apply}. The \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to calculate the delivery time in a reasonable response time. The detail of the process is out of scope of the paper.

Beside the translator, a proofreader selected by the client revises the final translation. As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language). The assessment is defined as a value between $1$ (very bad) and $5$ (perfect). As it is discussed in Section \ref{sec:apply}, it is used to evaluate and compare aggregation algorithms for translator's proficiency.

>>>>

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure \ref{fig:architecture}. The client submits a document and searches for translators with a specific target language. Based on the query document, the framework figures out the offered price, delivery time, proficiency of translators as well as the number of cooperation times related to each translator. The ranking system processes the calculated values and the offers the most related translators to the client.

@@

The \textit{Profiler} is responsible for accumulating translators' professional information,  offered price and translation duration per word. The \textit{Ranking} system uses Learning to Rank techniques to return the most related translators to the client. The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system. The evaluation system suggests three translators and the annotators rate them by comparing between their factors. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section \ref{sec:apply}. The \textit{Proficiency Estimator} system stores the previous-translated documents in the cloud and indexes them using Lucene. The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency. The proficiency value is compared by aggregating the similarity scores. The applied aggregation function is described in Section \ref{sec:apply}. The \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to calculate the delivery time in a reasonable response time. The details of the process are out of scope of the paper.

Beside the translator, a proofreader selected by the client revises the final translation. As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language). The assessment is defined as a value between $1$ (very bad) and $5$ (perfect). We use these assessments to evaluate and compare aggregation algorithms for translator's proficiency.

### 2014-03-08 docs/seminar/evaluation.tex
revising

In order to calculate the correlation value, we applied Spearman Rank Order and Kendall Rank Correlation as two common methods. Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using $181$ records of purchased orders. In addition it represents the Significance Test of both methods calculated by R.

@@

We use RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods. The library provides the  implementation of some Learning to Rank algorithms as well as evaluation measures in Java. By splitting the data in train, validation and test datasets, we use 5-Fold Cross-Validation on each run. One pointwise, three pairwise and two listwise methods are applied.

@@

Concerning the short final predicted list ($3$ items), every evaluator measure returns high result value even for a random ranker. This issue urges the need to run the evaluation on random data in order to find a baseline for comparison. We tackle the problem with two approaches. In the first approach, we run all the algorithms on data with random generated labels. In order to increase the accuracy of results, the process of generating randomized label is repeated $5$ times. The second approach is developing a simple ranker which randomly predicts the rank of each record.

@@

In addition to comparing the methods, features comparison can be an interesting point. Table \ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model. The coefficient value is a measure for understanding the importance of each feature in comparison to the others. As it is shown, price and delivery time seem to be the most effective features while the number of cooperation times has the lowest importance.

>>>>

By calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field. In the next step, in order to compare the algorithms, we test the correlation of each list with the proof-readers' feedbacks.

In order to calculate the correlation value, we applied Spearman Rank Order and Kendall Rank Correlation as two common methods. Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using $181$ records of purchased orders. In addition, it represents the Significance Test of both methods. For Spearman's test, p-values are computed using algorithm AS 89 \citep{as89}.

@@

We use the RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods. The library provides the  implementation of some Learning to Rank algorithms as well as evaluation measures in Java. By splitting the data in train, validation and test datasets, we use 5-Fold Cross-Validation on each run. One pointwise, three pairwise and two listwise methods are applied.

@@

Because of the short final predicted list ($3$ items), every evaluator measure returns high result value even for a random ranker. This issue urges the need to run the evaluation on random data in order to find a baseline for comparison. We tackle the problem with two approaches. In the first approach, we run all the algorithms on data with random generated labels. In order to increase the accuracy of results, the process of generating randomized label is repeated $5$ times. The second approach is developing a simple ranker which randomly predicts the rank of each record. In fact, the first tests whether there is anything to learn in the data and the second examines if the learning algorithms learn from the data.

@@

In addition to comparing the methods, features comparison can be an interesting point. Table \ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model. The coefficient value is a measure for understanding the importance of each feature in comparison to the others.

As it is shown, price and delivery time seem to be the most effective features while the number of cooperation times has the lowest importance. Surprisingly, proficiency plays a small role in the ranking of the translators. It can be because of the proposed business plan of the platform to the clients which guarantees an acceptable quality of translation. In addition, we expect that by applying the methods on much more amount of data, the proficiency feature gains more importance.

### 2014-03-08 docs/seminar/introduction.tex
revising

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.

@@

Ranking techniques are mostly one of the essential parts of IR frameworks. In recent years, Learning to Rank (L2R) has been studied extensively specially for document retrieval. It refers to machine learning techniques for training the model in a ranking task \citep{er}. In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \citep{l2r-intro}.

As well as ranking techniques, aggregation functions have a significant effect on the performance of IR systems. Aggregate tasks are those where documents' similarities are not
the final outcome, but instead an intermediary component. In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.

This paper addresses the problem of searching translators as experts. We have applied Learning to Rank in a candidate-based approach. Additionally, different aggregation algorithms related to documents of translators have been studied.

>>>>

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}  and not just traditional document retrieval. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.

@@

Ranking techniques are an essential part of each IR framework. In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval. It refers to machine learning techniques for training the model in a ranking task \citep{er}. In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \citep{l2r-intro}.

As well as ranking techniques, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
the final outcome, but instead an intermediary component. In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform. In contrast to common expert retrieval systems, we include significant factors of searching a translator (like price and delivery time) in the study as well as the relevance of the documents to the query document. We have applied Learning to Rank in a candidate-based approach. Additionally, different aggregation algorithms related to documents of translators have been studied.

### 2014-03-08 docs/seminar/methods.tex
revising

\section{Methods}
\label{sec:methods}
In this section, we study different methods and algorithms regarding to Aggregation Functions and Learning to Rank.

@@

The effect of different features on aggregation function is studied in \citet{agg-gp2}. As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$. Comparing query-based features using statistical measures, it inferred that the features may not, in general, be able to predict the optimal number of documents to aggregate for each query. Individual Expert Features is discussed in the next step. It is shown that relevant experts are associated with a higher ranked document than non-relevant experts. More interestingly, relevant experts are associated with less documents on average.

\citet{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise. Eleven data fusion as well as three statistically different document weighting were tested. In practice, the approach considers both number of documents and expert features regarding to the ranking score of the documents. The results show that while some of adapted voting techniques are most likely outperform others, the proposed approach is effective when using appropriate one.

@@

\subsection{Learning To Rank}
Learning to rank refers to machine learning techniques for training the model in a ranking task. Due to its importance, learning to rank has been drawing broad attention in the machine learning community recently.

In learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied. As \citet{l2r-intro} points out the relation between learning to rank and ordinal classification, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.

@@

A critical point in all kinds of information retrieval systems is evaluation of results. The evaluation on the performance of a ranking model is carried out by comparison between the ranking lists output of the model and the ranking lists given as the ground truth. Some common IR evaluation methods like Mean average precision (MAP), [Normalized] Discounted Cumulative Gain ([N]DCG), Mean Reciprocal Rank (MRR) are also widely user in leaning to rank evaluation. Among the mentioned metrics, DCG/NDCG is the only one used for graded relevance.

Recently, \citet{l2r-err} have proposed a new evaluation metrics called Expected Reciprocal Rank (ERR) which claims to model user's satisfaction with search results better than the DCG metric. \citet{l2r-err} addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it. It asserts that based on research on modeling user click behavior \citep{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list. In other words, it assumes that a user is more likely to stop browsing if they have already seen one or more highly relevant documents. By presenting ERR formula in \cite{l2r-err}, it claims that results reflects real user browsing behavior better and quantifies user satisfaction more accurately than DCG.

>>>>

\section{Methods and Related Work}
\label{sec:methods}
In this section, we study different methods and algorithms regarding to Aggregation Functions and Learning to Rank.

@@

The effect of different features on the aggregation function is studied in \citet{agg-gp2}. They show that the number of documents is an important factor, such that the performance of different queries are optimal for different values of $N$. Comparing query-based features using statistical measures, they infer that the document features (such as TF, IDF) may not, in general, be able to predict the optimal number of documents to aggregate for each query. In contrast, individual Expert Features have been shown to be more informative such that relevant experts are associated with a higher ranked document than non-relevant experts. More interestingly, relevant experts are associated with less documents on average.

\citet{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise. Eleven data fusion methods as well as three statistically different document weighting models were tested. In practice, the approach considers both the number of documents and expert features regarding to the ranking score of the documents. The results show that while some of adapted voting techniques most likely outperform others, the proposed approach is effective when using the appropriate one.

@@

\subsection{Learning To Rank}
Learning to rank refers to machine learning techniques for training the model in a ranking task. Due to importance of ranking problems, learning to rank has been drawing broad attention in the machine learning community recently.

In the learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied. As \citet{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.

@@

A critical point in all kinds of information retrieval systems is the evaluation of results. The evaluation on the performance of a ranking model is carried out by comparison between the ranking lists output of the model and the ranking lists given as the ground truth. Some common IR evaluation methods like Mean average precision (MAP), [Normalized] Discounted Cumulative Gain ([N]DCG), Mean Reciprocal Rank (MRR) are also widely user in leaning to rank evaluation. Among the mentioned metrics, DCG/NDCG is the only one used for graded relevance.

Recently, \citet{l2r-err} have proposed a new evaluation metrics called Expected Reciprocal Rank (ERR) which claims to model user's satisfaction with search results better than the DCG metric. \citet{l2r-err} addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it. It asserts that based on research on modeling user click behavior \citep{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list. In other words, it assumes that a user is more likely to stop browsing if they have already seen one or more highly relevant documents. Introducing the ERR formula, \cite{l2r-err} claim that results reflect real user browsing behavior better and quantifies user satisfaction more accurately than DCG.
